Manuscript Figures

### 2024-05-29 Manuscript_Figures.Rmd
Update example mapcode figure

```{r}
library(here)
library(tidyverse)
library(terra)
library(tidyterra)
library(ggthemes)
library(ggpattern)
```

@@

mapcodes %>%
  ggplot() +
  geom_hline(yintercept = 600, linetype = "dashed") +
  geom_vline(xintercept = 200, linetype = "dashed") +
  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=16) +
  scale_color_colorblind() +
  coord_equal() +
  labs(X = "X (m)",
       Y = "Y (m)",
       color = "Species") +
  theme_bw()
#TODO: Replace species codes with species names
```

>>>>

```{r}
library(here)
library(tidyverse)
library(terra)
library(tidyterra)
library(ggthemes)
library(ggpattern)
library(sf)
```

@@

mapcodes_vect <- vect(mapcodes, geom=c("X", "Y"), crs="", keepgeom=FALSE)

tree_polys <- list()
for(i in 1:nrow(mapcodes_vect)){
  tree_i <- mapcodes_vect[i,]
  buffer_i <- buffer(tree_i, width = mapcodes_vect$CD_m[i]/2)
  tree_polys[[i]] <- buffer_i
}
mapcodes_poly <- vect(tree_polys)
writeVector(mapcodes_poly, here("Plots","sample_mapcode_canopies.shp"))
mapcodes_poly <- arrange(mapcodes_poly, CD_m)

example_mapcode <- ggplot() +
  geom_hline(yintercept = 600, linetype = "dashed") +
  geom_vline(xintercept = 200, linetype = "dashed") +
  geom_spatvector(data=mapcodes_poly, aes(fill=SPECIES_SYMBOL, color=SPECIES_SYMBOL), alpha=0.7) +
  scale_fill_colorblind() +
  scale_color_colorblind() +
  labs(x = "X (m)",
       y = "Y (m)",
       fill = "Species",
       color="Species") +
  theme_bw()
example_mapcode
ggsave("example_mapcode.jpg",path = here("Plots"))

#TODO: Replace species codes with species names
```
